Information Disclosure Concerns in The Age of Wearable Computing

### 2016-01-29 USEC2016-camera-ready/tex-inputs/appendixes.tex
added a missing period
fixed errors in appendix

\section{Omitted Survey Questions}
\label{sec:noquestions}
Our participants answered four additional question which are not detailed in this paper. Two questions compared smartphones to wearable devices, to investigate if participants inherently saw wearables as threatening due to its unfamiliarity. The questions were not particularly well suited for this task, and our results showed no significant difference between smartphone and wearables perceptions. The other two questions asked our participants to numerically rate the risks and benefits of common, familiar technologies versus wearables (e.g., an airplane versus a wearable). In addition to the fact that these comparisons were unsound to make, our results largely highlighted our participants' unfamiliarity with wearables or other less common devices; participants rated more familiar technologies as more beneficial or risky.

\section{Coding Label Definitions}
\label{sec:coding}
Researchers coded the self reported answers as follows:\\
{\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
{\bf Security}:  ``security,'' mention of malware, hacking. \\
{\bf GPS tracking}: ``location,'' ``GPS,'' mention of monitoring. \\
{\bf Being Unaware}: mention of using, collecting, and disclosing data without permission. \\
{\bf False information}: inaccurate or maliciously false data.\\
{\bf Health Risk}: mention of radiation, cancer, or other effects.\\
{\bf Safety}: mention of distractions causing car crashes and injuries, violence due to the device, injuries from malfunctions.\\
{\bf Discomfort}: mention of eye strain, headache, irritation. \\
{\bf Financial cost}: cost of buying or using the device. \\
{\bf Theft}: mention of device theft. \\
{\bf Social Impact}: mention of dependency, distance from people, changes in decision making, etc. \\
{\bf Social Stigma}: mention of judgment, hate, or bystanders.\\ 
{\bf Aesthetics}: mention of fashion or looking dorky. \\
{\bf Miscellaneous}: odd comments, uncommon concerns. \\
{\bf None}: ``None,'' mention of no threat, or no real concerns \\
{\bf Don't know}: ``do not know,'' general confusion \\
{\bf Don't care}: `` do not care,'' nonchalant answers

>>>>

\noindent {\bfseries Omitted Survey Questions}
\label{sec:noquestions}
Our participants answered four additional questions not detailed in this paper. Two questions compared smartphones to wearable devices, to investigate if participants inherently saw wearables as threatening due to its unfamiliarity. The questions were not particularly well suited for this task, and our results showed no significant difference between smartphone and wearables perceptions.

The other two questions asked participants to numerically rate risks and benefits of familiar technologies versus wearables (e.g., an airplane versus a wearable). This was to mimic the methodology in Fischhoff's seminal study on attitudes toward technological risks and benefits. In Fischhoff's study \cite{fischhoff1978safe}, all technologies were concerning with physical risk, while ours mixed information disclosure risks with physical risks. These comparisons were unsound to make. Nonetheless, our results largely highlighted participants' unfamiliarity with devices; generally, participants rated more familiar technologies as more beneficial or risky. \\

\noindent {\bfseries Coding Label Definitions}
\label{sec:coding}
To give some transparency into how we coded the answers (ranging from 1 to 1,400+ words), we provide the coding outline we used. An answer mentioning multiple concerns was given multiple coding labels. \\

\noindent {\bf Privacy}: ``privacy,'' mention of personal details, spying. \\
{\bf Security}:  ``security,'' mention of malware, hacking. \\
{\bf GPS tracking}: ``location,'' ``GPS,'' mention of monitoring. \\
{\bf Being Unaware}: mention of using, collecting, and disclosing data without permission. \\
{\bf False information}: inaccurate or maliciously false data.\\
{\bf Health Risk}: mention of radiation, cancer, or other effects.\\
{\bf Safety}: mention of distractions causing car crashes and injuries, violence due to the device, injuries from malfunctions.\\
{\bf Discomfort}: mention of eye strain, headache, irritation. \\
{\bf Financial cost}: cost of buying or using the device. \\
{\bf Theft}: mention of device theft. \\
{\bf Social Impact}: mention of dependency, distance from people, changes in decision making, etc. \\
{\bf Social Stigma}: mention of judgment, hate, or bystanders.\\ 
{\bf Aesthetics}: mention of fashion or looking dorky. \\
{\bf Miscellaneous}: odd comments, uncommon concerns. \\
{\bf None}: ``None,'' mention of no threat, or no real concerns \\
{\bf Don't know}: ``do not know,'' general confusion \\
{\bf Don't care}: `` do not care,'' nonchalant answers
